
\documentclass[a4paper,8pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{Arial}  % Set it to whatever you like

\begin{document}

% non-numbered pages
\pagestyle{empty} 


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Anuj Kumar Chaudhary} \\[6pt]
\\
\textcolor[HTML]{371e77}{\underline{\href{mailto:anuj.kumarchaudhary038@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} anuj.kumarchaudhary038@gmail.com}} $|$}
\textcolor[HTML]{371e77}{\underline{\href{mailto:anuj.2024ec1144@kiet.edu}{\raisebox{-0.05\height}{\faEnvelope} anuj.2024ec1144@kiet.edu}} $|$}
\textcolor[HTML]{371e77}{\href{tel:+919807145009}{\raisebox{-0.05\height}{\faMobile} +91 9807145009}}

\textcolor[HTML]{371e77}{\underline{\href{https://github.com/akc2531}{\raisebox{-0.05\height}{\faGithub} github.com/akc2531}} $|$}
\textcolor[HTML]{371e77}{\underline{\href{https://www.linkedin.com/in/anuj-kumar-chaudhary-analytics/}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/anuj-kumar-chaudhary-analytics/}}}
\end{tabularx}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{KIET Group of Instituions} & \hfill \color[HTML]{371e77} Expected graduation date: Jun. 2024 \\
\color[HTML]{371e77} B.Tech. in Electronics and Communication Engineering$|$ {\uline{\href{https://akc2531.github.io/MyPortfolio/}{Link to all courses}}} & \hfill \color[HTML]{4B28A4} \textit{\textbf{Percentage: 74.29}} \\
\color[HTML]{1C033C} \textbf{St. Basil's School, Basti} & \hfill \color[HTML]{371e77} | 2019 \\
\color[HTML]{371e77} Senior Secondary(CISCE)  & \hfill \color[HTML]{4B28A4} \textit{\textbf{Percentage: 84.80}} \\
\color[HTML]{1C033C} \textbf{St. Basil's School, Basti} & \hfill \color[HTML]{371e77} | 2017 \\
\color[HTML]{371e77} Secondary(CISCE)  & \hfill \color[HTML]{4B28A4} \textit{\textbf{Percentage: 83}} \\
\end{tabularx}


%Experience
\section{Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{\href{https://akc2531.github.io/MyPortfolio/}{IBM}}} \hfill \color[HTML]{371e77} 12th June,2023  -  24th July,2023 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Frontend Development}}\ \hfill \color[HTML]{4B28A4} \textit{HTML, CSS, Javascript, GitHub} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Responsible for developing Frontend web applications based on HTML, CSS and JavaScript.
        \item Independently tackled the challenge of crafting a responsive 
  website tailored for mobile platforms, and meticulously refined the CSS to achieve a more polished and efficient design.
        \item Learnt how to deploy web applications.
        \item Worked on key technologies like Javascript, HTML and CSS.
    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{{CISCO(VIRTUAL)}}} \hfill \color[HTML]{371e77} 12th May. 2023 - 10th June. 2023 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Cyber security Trainee}}\ \hfill \color[HTML]{4B28A4}  \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item As a Cybersecurity trainee, I typically undergo training and development programs to acquire the necessary skills and knowledge in the field of cybersecurity
        \item  I was trained on promoting security awareness among employees and stakeholders.
    \end{itemize}
\end{minipage}
\end{tabularx}

% Projects
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://github.com/akc2531/COALMINERS}{Smart Helmet for Coal Miners}}} \hfill \color[HTML]{371e77} Jul. 2023 - Ongoing \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Coal Miner Sensor Monitoring System }} \hfill \color[HTML]{4B28A4} \textit{ JavaScript, HTML, CSS, ThingSpeak, Arduino IDE} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Utilizes MQ2, MQ3, MQ7, and DHT22 sensors to measure environmental parameters.
        \item ESP32 Microcontroller is used to collect sensor data.
        \item Real-time data visualization through a locally hosted web page created with HTML, CSS, and JavaScript.
        \item Data transmission to ThingSpeak Cloud for remote monitoring and analysis.
        \item Wireless monitoring through ESP8266, connected to the same server, enabling data visualization on gloves-mounted LCD screens.
    \end{itemize}
    \end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://akc2531.github.io/MyPortfolio/}{Portfolio Website}}} \hfill \color[HTML]{371e77} June 2023 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Responsive Portfolio Website}} \hfill \color[HTML]{4B28A4} \textit{ JavaScript, HTML and CSS} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Responsive Design: The website is designed to adapt to various screen sizes, ensuring a great user experience on both mobile and desktop devices.
        \item Interactive Content: Engage your visitors with interactive content, including smooth scrolling, animated sections, and dynamic skill bars.
        \item About Me Section: Share your background, skills, and experience to give visitors a better understanding of who you are.
        \item Contact Information: Provide your contact details and links to your social profiles, making it simple for others to get in touch.
    \end{itemize}
    \end{minipage}
\end{tabularx}

\section{Skills}
\color[HTML]{1C033C}\textbf{Languages:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} Java, CSS, HTML, SQL, Beginner in JavaScript, Time Management, Leadership\\[3pt]
\color[HTML]{1C033C}\textbf{Certifications:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} \uline{\href{https://trainings.internshala.com/verify-certificate/?certificate_number=cnzk0h47ptr}{Internshala: Core Java}}.


\section{Achievements}
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item 4-star Java coder on hackerrank
        \item Secured 2nd position in IntraCollege technical Quiz competition
    \end{itemize}
    \end{minipage}
\end{document}

